\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in R

### 2014-01-15 papers/jss/article.Rnw
Revert back to my motivating question to start the second paragraph of the introduction "Given these requirements, how do we X, Y, Z?"
This to me is much more engaging than the text that replaced it, and
motivating questions like this are not uncommon in JSS introductions.

The next sentence, "Most technical computing languages such as X, Y,
Z, and W" does not seem as correct as the simpler "Programming
languages X, Y, Z, and W" that I used previously.  X, Y, Z, and W do
not necessarily equate with "most technical computing languages", and
"technical computing languages" is more cumbersome tha

Modern data collection and analysis pipelines increasingly involve collections
of decoupled components in order to better manage software complexity 
through reusability, modularity, and fault isolation \citep{Wegiel:2010:CTT:1932682.1869479}.
% This is really a different pattern not connected well here.
%Data analysis patterns such as Split-Apply-Combine
%\citep{wickham2011split} explicitly break up large problems into manageable pieces.  
These pipelines are frequently built using different programming 
languages for the different phases of data analysis -- collection,
cleaning, modeling, analysis, post-processing, and
presentation in order to take advantage of the unique combination of
performance, speed of development, and library support offered by
different environments and languages.  Each stage of such a data
analysis pipeline may produce intermediate results that need to be
stored in a file or sent over the network for further processing. 
% JO Perhaps also mention that serialization is needed for distributed
% systems to make systems scale up?

Such systems require reliable and efficient exchange of intermediate
results between the individual components, using formats that are
independent of platform, language, operating system or architecture.
Most technical computing languages such as R, Julia, Java, and Python
include built-in support for serialization, but the default formats 
are usually language specific and thereby lock the user into a single
environment.

>>>>

Modern data collection and analysis pipelines increasingly involve collections
of decoupled components in order to better manage software complexity 
through reusability, modularity, and fault isolation \citep{Wegiel:2010:CTT:1932682.1869479}.
% This is really a different pattern not connected well here.
%Data analysis patterns such as Split-Apply-Combine
%\citep{wickham2011split} explicitly break up large problems into manageable pieces.  
These pipelines are frequently built using different programming 
languages for the different phases of data analysis -- collection,
cleaning, modeling, analysis, post-processing, and
presentation in order to take advantage of the unique combination of
performance, speed of development, and library support offered by
different environments and languages.  Each stage of such a data
analysis pipeline may produce intermediate results that need to be
stored in a file or sent over the network for further processing. 
% JO Perhaps also mention that serialization is needed for distributed
% systems to make systems scale up?
% MS: yes perhaps somewhere near here we could define serialization
% and describe this.

Given these requirements, how do we safely and efficiently share intermediate results
between different applications, possibly written in different
languages, and possibly running on different computer systems?
% Reverted to my original above, because the replacement below puts me
% to sleep:
%Such systems require reliable and efficient exchange of intermediate
%results between the individual components, using formats that are
%independent of platform, language, operating system or architecture.
Programming
languages such as R, Julia, Java, and Python include built-in
support for serialization, but the default formats 
are usually language specific and thereby lock the user into a single
environment.
